---
title: "Short Guide Nonlinear Optimization Package"
author: "Bruna Queiroz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## INTRODUCTION

This is a short guide for adapting functions, constraints and parameters used in experiments to search the optimum solution (or approximation) of restricted and unrestricted nonlinear optimization problems. 

## LISTS AND PARAMETERS

Some parameters passed to the functions inside the package need to have a specific format to ensure the correct results and the correct operantion of them.

### Parameter "x.list"

In the _backtracking_, _gradientproj_, _quasiNewton_ functions the user must have information about the initial point for the method to perform a search for the optimal point of the objective function. 

This information must be passed in the form of a list that must contain the starting point, function value, and gradient evaluated at that point. In _grandientproj_ and _quasiNewton_, there is verification of the correct format of the list, if the user pass only the value of the point, the function *check_parameters* creates a complete list with all the necessary.

```{r cars}

```

### Parameter "obj.list"

"obj.list" is a list that has two important instances for the non-linear optimization methods: _obj_, which is the objective function for non-linear optimization and _df_, the objective function gradient in the format of a function.  

In _gradientproj_ and _quasiNewton_, there is the verification of the _obj.list_. If the objective function is passed, the function *check_parameters* creates a complete list with the _df_ function, which uses the default gradient function for central finite differences, if the user wants to modify parameters for calculation of the numerical gradient it must be passed int the "..." from the calls of a _gradientproj_ and _quasiNewton_.

### Parameter "constraint"
This list is necessary for functions with box constraints and has the following elements: _xmin_ and _xmax_. The function _hjalgorithm_ could be use both for functions under constraints and unconstraints problems. Thus, when is not passed for the function the constraints, it is considered that $xmin = -Inf$ and $xmax = +Inf$. 


## IMPORTANT NOTES

### Maximum number of iterations
